HSF Community White Paper on Data Organization, Management and Access (DOMA)

### 2018-03-22 CWP/papers/HSF-CWP-2017-04_doma/latex/hsf-cwp-dm.tex
DOMA CWP: reintegrate lost modifications from Bo

\subsection{Event-based granularity}\label{event-based-granularity}
Can this be implemented efficiently, scalably and in a cost-effective manner
for relevant use cases (reco, simulation, event-picking)? Does it
provide an advantage over current file-based granularity?

@@

\emph{Should be completed by
2020: actions can be done in parallel}.

\subsection{Data organization and analysis
technologies}\label{data-organization-and-analysis}
How can we benefit from technologies adopted by the
big-data world?

@@

\subsection{Data caching}\label{data-caching}
What role will
caching play to use compute resources and what technologies will be
used?

@@

\emph{First two actions to be completed by 2020, CDN/NDN evaluation more long-term}

\subsection{Getting the most out of the
storage diversity}\label{storage-diversity}
how to minimize HEP infrastructure cost by
exploiting varied quality of service from different storage
technologies?

>>>>

\subsection{Sub-file granularity}\label{sub-file-granularity}
Sub-file granularity ({\it e.g.} event-based granularity) should be studied to see
whether it can be implemented efficiently and in a scalable, cost-effective manner for
all use cases that rely on event selection and whether it offers an advantage over
the current paradigm of file-based granularity.

@@

\emph{The previous tasks should be completed by 2020 (and can be performed in parallel).}

\subsection{Data organization and analysis
technologies}\label{data-organization-and-analysis}
Data organization and analysis technologies in use by other big data users should be
studied to glean whether we can benefit from them.

@@

\emph{The proposed proof-of-concept involves the previous tasks that should be completed by 2020. If successful,
implementation as a production system will be done in the following years.}

\subsection{Data caching}\label{data-caching}
Investigate the role that data placement optimizations, such as caching,
can play in optimizing the use of computing resources as well as the
technologies that can be used for this.

@@

\emph{The first two actions should be completed by 2020 but CDN/NDN
evaluation is more long-term}

\subsection{Getting the most out of the
storage diversity}\label{storage-diversity}
How to minimize HEP infrastructure cost by
exploiting varied quality of service from different storage
technologies?
